---
title: "Multivariate analysis"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

author: "Carlos"
date: "02/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Multivariate Analysis of Network data

Note: This tutorial is bascially the same as the on described in "Protocol_multivariate.R". Either download the repo or, much easier, just copy the script and paste into your r script.

## Intro & Basics

The question addressed here is whether network traits "cluster" according to species identity
For this we are using:

  * PCA: To visualize whether there is any clustering
  * RDA: To obtain a p-value associated to those clustering (in other words whether those
     cluster are "significantly" different from each other). That said the wording
     "significantly different" is becoming controversial

To do that I use base R functions combined with functions from three other packages: vegan, tidyverse and RColorBrewer
You might need to install those packages. You can do that via R studio or: 

```{r, eval=FALSE}
install.packages("vegan")
install.packages("tidyverse")
install.packages("RColorBrewer")

```

## 1. Loading files.

Note: one can load directly excel files (.xlxs) using R studio. This is a relatively new
feature. I am used to the function "read.csv" for which I need to save the excel sheet I am interested as
a csv file first. In this case, I saved the "edge" sheet of each excel file of each of the 7 species as .csv

```{r }
temp = list.files(path="processedData\\",pattern="*.csv")
temp<-paste("processedData\\",temp,sep = "")
myfiles = lapply(temp,function(x){read.csv(x,header = TRUE,stringsAsFactors = FALSE)} )
Fung_Netw_Traits<-do.call(rbind,myfiles)
```

## 2. Getting to know the data.

### 2.1 How R sees the data. 
It is useful to have an idea on how R recognize the data. R is an "object oriented"
program language. That is, every data is an object which has certain properties. R uses these properties to 
categorized the object. It is useful to know what kind of object is your data because some functions only work
on one object type but not in others.


```{r}
str(Fung_Netw_Traits)
```

### 2.2. Looking at the distribution of the data. 
More impotantly, what is the distribution of the data? 
To simply get means, min, max per fungal species:

```{r}
aggregate(
        Fung_Netw_Traits[which(Fung_Netw_Traits$Type=="E"),#Removing the edges in the feature
                         c("Length","Width","Area","Volume","Resistance_2","Tortuosity","Or_ij","Betweenness","Accessibility")],
        by=list(Fung_Netw_Traits[which(Fung_Netw_Traits$Type=="E"),]$name),
        range)#You can try functions other than "range". For example: "min", "max", "median" ; "summmary" is good because it gets you more than one summary statistics, but it can be confusing with so much data.
```


Visualinzing as simple historgrams helps. To make those, I use the suite of functions in the package tidyverse.

```{r,message=FALSE}
library(tidyverse)
```

First, reorganizing the dataframe helps so the figures are made easier

```{r}
Re_org<-
        Fung_Netw_Traits%>%
        filter(Type=="E")%>%
        select(c("name","Length","Width","Area","Volume","Resistance_2",
                 "Tortuosity","Or_ij","Betweenness","Accessibility"))%>%
        group_by(name)%>%
        gather(key=variable,
               value=value,Length:Accessibility)
```        
        

Now we can make simple histograms (because there are too many variables, zoom the graphic to better see)

NOTE: I know, you can see nothing here, but when you run this in your r session and zoom in, you can check each histogram
```{r,echo = FALSE,message=FALSE}
Re_org%>%
        ggplot()+
        aes(value,fill=name)+
        geom_histogram()+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 9)+
        theme(legend.position = "none")
```

Or as density plots

```{r,message=FALSE}
Re_org%>%
        ggplot()+
        aes(value,fill=name)+
        geom_density(alpha=0.6)+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 9)+
        theme(legend.position = "none")
```

Or combining histograms and density plots

NOTE: I decided to remove the headers on each histogram so you
can see something here. Check the comment in the code.

```{r,message=FALSE}
Re_org%>%
        ggplot()+
        aes(value,fill=name)+
        geom_histogram(aes(y=..density..), position="identity", alpha=0.5)+
        geom_density(alpha=0.6)+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 9)+
        theme(legend.position = "none",
              strip.text.x = element_blank())#because I want to save it I am removing the labels in each panel, then I can use illustrator or inkscape to add them manually
```

Form these plots one learns that:

  * The distribution of the data for a given variable is similar across species.
  * Almost all variables are right skewed (long right tail). Some more than others:
    + Less skewed: "Accessibility","Area","Length","Width" (althouhg width has two peaks)
    + Highly skewed: "Betweenness","Resistance_2","Tortuosity","Volume"
  * Orientation has three peaks (this one will be tricky)
       

The following are the same plots, just splitted so it is easier to check the data. Again here, I am not printing headers to better check things

Right skewed (but not so much)

```{r,message=FALSE}
Re_org%>%
        filter(variable %in% c("Accessibility","Area","Length","Or_ij","Width"))%>%
        ggplot()+
        aes(value,fill=name)+
        geom_histogram(aes(y=..density..), position="identity", alpha=0.5)+
        geom_density(alpha=0.6)+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 5)+
        theme(legend.position = "none",
              strip.text.x = element_blank())#because I want to save it I am removing the labels in each panel, then I can use illustrator or inkscape to add them manually
```

Highly right skewed (like Poisson distribution)
```{r,echo = FALSE}
Re_org%>%
        filter(variable %in% c("Betweenness","Resistance_2","Tortuosity","Volume"))%>%
        ggplot()+
        aes(value,fill=name)+
        geom_histogram(aes(y=..density..), position="identity", alpha=0.5)+
        geom_density(alpha=0.6)+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 4)+
        theme(legend.position = "none",
              strip.text.x = element_blank())#because I want to save it I am removing the labels in each panel, then I can use illustrator or inkscape to add them manually
```

### 2.3 Data transfomation

So, I tried the log10 (Betweenness,Length,Volume,Reistance,Tortuosity) and sqrt (Area) tranformation. 
It does not make it normal but it helps making them less skewed. As you can see I had to add 0.325 in 
some cases because of zero´s):

```{r,message=FALSE}
Fung_Netw_Traits%>%
        filter(Type=="E")%>%
        select(c("name","Length","Width","Area","Volume","Resistance_2",
                 "Tortuosity","Or_ij","Betweenness","Accessibility"))%>%
        mutate(Betweenness=log10(Betweenness+0.325))%>%
        mutate(Area=sqrt(Area+0.325))%>%
        mutate(Volume=log10(Volume+0.325))%>%
        mutate_at(c("Length","Resistance_2","Tortuosity"),log10)%>%
        group_by(name)%>%
        gather(key=variable,
               value=value,Length:Accessibility)%>%
        ggplot()+
        aes(value,fill=name)+
        #geom_histogram(aes(y=..density..), position="identity", alpha=0.5)+
        geom_density(alpha=0.6)+
        facet_wrap(name ~ variable, scales = "free",nrow = 7,ncol = 9)+
        theme(legend.position = "none")

```

## 3. Preparing the functions and data for PCA

### 3.1 Loading vegan package

Note: Other functions from other packages are also available to do a PCA. rda from vegan is the one I am used to.

```{r,message=FALSE}
library(vegan)

```
### 3.2 Subsetting and transforming the data 

To run a simple PCA with the rda function is necessary to only feed an object of type "matrix" or "dataframe" with the 
varialbes one is interested and that are appropriate for a PCA (statistically speaking). 
In general PCA is well suited for data that is continuous and that follows more or less normal distribution. 
This excludes: count data, proportions, categorical variables.

Dataframe using raw data
```{r}
Hyphae_char_raw<- Fung_Netw_Traits[which(Fung_Netw_Traits$Type=="E"),#Removing the edges in the feature
        c("Length","Width","Area","Volume","Resistance_2","Tortuosity","Or_ij","Betweenness","Accessibility")]
          #selecting only "descriptive" hyphal parameters that are numeric
```

Dataframe using transformed data (as described above)
```{r}
Hyphae_char_trans<-Fung_Netw_Traits%>%
        filter(Type=="E")%>%
        select(c("Length","Width","Area","Volume","Resistance_2",
                 "Tortuosity","Or_ij","Betweenness","Accessibility"))%>%
        mutate(Betweenness=log10(Betweenness+0.325))%>%
        mutate(Area=sqrt(Area+0.325))%>%
        mutate(Volume=log10(Volume+0.325))%>%
        mutate_at(c("Length","Resistance_2","Tortuosity"),log10)
```

Creating a unique ID for each row in the datataframes
```{r}
Hyphae_ID<-Fung_Netw_Traits[which(Fung_Netw_Traits$Type=="E"),c("name","Name")]
Hyphae_ID<-paste(Hyphae_ID$name,Hyphae_ID$Name,sep = "_")

#Adding this ID as rownames
rownames(Hyphae_char_raw)<-Hyphae_ID

rownames(Hyphae_char_trans)<-Hyphae_ID

```
## 4 Performing a PCA

Just need to run the rda function (As simple as that). In these cases I save the anaylsis so I can plotted (see below)

```{r}
Hyphae_pca<-rda(Hyphae_char_raw,scale = TRUE)
#scale =TRUE standarize variances since each variable has a different scale

Hyphae_pca_trans<-rda(Hyphae_char_trans,scale = TRUE)

```
### Plotting the results

Vegan comes with its own ploting functions. One is biplot.rda (or simply biplot)
The plots are not so nice looking. I will use later other functions

I like to displayed each fungus with a color in the plot. To do this, I created a factor vector with the names of the seven fungi used and add a color code to each. (this is completely optional)

```{r}
Fungi<-as.factor(Fung_Netw_Traits[which(Fung_Netw_Traits$Type=="E"),c("name")])
#And then adding "color" to those fungi
library(RColorBrewer)#You might need to install this package
colvec<-brewer.pal(n = 7, name = "Set1")#This is pure aesthetics, 
#I like the color combinations in "Set1" that come in the package
#RcolorBrewer. I chose 7 color because there are 7 fungi
```

Ploting PCA with raw data

```{r,message=FALSE}
#Making the basic PCA plot
biplot(Hyphae_pca,scaling = 2,
        display = "species", 
        type = "text")
       
#Adding a lenged with the names of the fungi (colored)
legend("topright", legend = levels(Fungi), bty = "n",
       col = colvec, pch = 21, pt.bg = colvec,xjust=1,pt.cex = 2)

# Adding the points, which in this case correspon to each hyphae
points(Hyphae_pca, display = "sites", 
       col = colvec[Fungi],
       scaling = 2, pch = 21, bg = colvec[Fungi])

```

Ploting PCA with transformed data

```{r,message=FALSE}
#Making the basic PCA plot
biplot(Hyphae_pca_trans,scaling = 2,
       display = "species", 
       type = "text")

#Adding a lenged with the names of the fungi (colored)
legend("topright", legend = levels(Fungi), bty = "n",
       col = colvec, pch = 21, pt.bg = colvec,xjust=1,pt.cex = 2)

#Adding the points, which in this case correspon to each hyphae
points(Hyphae_pca, display = "sites", 
       col = colvec[Fungi],
       scaling = 2, pch = 21, bg = colvec[Fungi])

```


